Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-10 longoutput.tex
Fix edge case bug for gates propagation
Remove useless subscript

Here we describe the scheme between the classical client and an honest quantum server. This is similar to the underlying construction for \cite{mahadev_delegation}. We first preprocess the circuit using tools such as \cite{quant-ph/0301040}. We then follow \cite{kitaev2002classical} to reduce the problem to an instance of local Hamiltonian. We then analyze it using tools from \cite{PhysRevA.93.022326}. Then, NYI cuz we're stuck.

@@

We consider the transform $T(\ket{\psi})=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$T\circ H_f=H_f\circ T$$
$$T\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ T=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ T$$
Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.

@@

Then, we ensure that the gates are applied correctly.
$$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
	+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
	-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$

>>>>

Here we describe the scheme between the classical client and an honest quantum server. This is similar to the underlying construction for \cite{mahadev_delegation}. We first preprocess the circuit using tools such as \cite{quant-ph/0301040}. We then follow \cite{kitaev2002classical} to reduce the problem to an instance of local Hamiltonian. Using tools from \cite{PhysRevA.93.022326}, the local Hamiltonian is written in a simple form. Then, NYI cuz we're stuck.

@@

We consider the transform $T(\ket{\psi})=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$T\circ H=H\circ T$$
$$T\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ T=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ T$$
Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.

@@

Then, we ensure that the gates are applied correctly.
$$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
	+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
	-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
Extra care must be taken for boundary cases.
$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
